Final Report

### 2022-05-06 Final Report.Rmd
i put head so the html didn't run forever but it only shows one of the two countries we can fix this later

>>>>

Combine the data based on continent.

```{r}
joined_all <- right_join(deaths_df, world_pop, by=c('country' = 'Country.Name', 'year' = 'Year'))
head(joined_all)

north_america <- joined_all %>% filter(country %in% c("United States", "Canada"))
head(na.omit(north_america))

south_america <- joined_all %>% filter(country %in% c("Brazil", "Chile"))
head(na.omit(south_america))

africa <- joined_all %>% filter(country %in% c("Nigeria", "Malawi"))
head(na.omit(africa))

europe <- joined_all %>% filter(country %in% c("Germany", "Serbia"))
head(na.omit(europe))

asia <- joined_all %>% filter(country %in% c("Pakistan", "Sri Lanka"))
head(na.omit(asia))

oceania <- joined_all %>% filter(country %in% c("Australia", "New Zealand"))
head(na.omit(oceania))
